Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension

### 2018-05-29 EMNLP-demo-paper/system.tex
add prediction section

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{sentence}
 \caption{
The interface for showing input sentences. The user can manually alter the words or apply automatic perturbation/paraphrasing of the inputs. In the \emph{perturbed} dropdown menu, the blue words are the only not exist in the original sentence.
 }
\label{fig:sentence}
\end{figure}

@@

\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{attentionPanels}
  \vspace{-6mm}
 \caption{
Attention visualization. In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value. In the matrix attention view (b), the entries of $i^{th}$ row represent the probabilities of words in hypotheses align to the $i^{th}$ word in the premise.
The user can alter the attention values via the pop-up interface illustrated in (c).
We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentence based on the dependency tree.
%
For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d).
}
\label{fig:attentionVis}
\end{figure*}

@@

\subsection{Prediction Summarization}

>>>>

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=0.9\linewidth]{sentence}
 \caption{
The interface for showing input sentences. The user can manually alter the words or apply automatic perturbation/paraphrasing of the inputs. In the \emph{perturbed} dropdown menu, the blue words are the only not exist in the original sentence.
 }
\label{fig:sentence}
\end{figure}

@@

@@

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=0.8\linewidth]{prediction}
 \caption{
Summarize the prediction results of the perturbed input for the natural language inference model.
the prediction is encoded as a point in the barycentric coordinate system of the triangle, in which each vertex corresponds to one prediction label, namely, \emph{entail}, \emph{contradict}, and \emph{neutral}.
 %
 }
\label{fig:prediction}
\end{figure}

\subsection{Prediction Visualization}

The prediction result for the original sentence pair is represented by a larger yellow circle and the prediction of perturbed pairs are illustrated by smaller grey circles.

A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.

\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=0.9\linewidth]{attentionPanels}
  \vspace{-3mm}
 \caption{
Attention visualization. In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value. In the matrix attention view (b), the entries of $i^{th}$ row represent the probabilities of words in hypotheses align to the $i^{th}$ word in the premise.
The user can alter the attention values via the pop-up interface illustrated in (c).
We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentence based on the dependency tree.
%
For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d).
}
\label{fig:attentionVis}
\end{figure*}
